Towards human SuperEEG

### 2018-10-10 paper/main.tex
small changes in read through

We designed our approach to be agnostic to electrode impedances, as
electrodes that do not exist do not have impedances.  Therefore our
algorithm recovers voltages in standard deviation ($z$-scored) units
rather than attempting to recover absolute voltages. (This property
reflects the fact that $\hat{K}_{\beta_s, \alpha_s}$ and
$\hat{K}_{\alpha_s, \alpha_s}$ are correlation matrices rather than
covariance matrices.)  Also, note that
Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$
matrix, which can become computationally intractable when $T$ is very
large (e.g., for the patient highlighted in Fig.~\ref{fig:recon}, $T =
20458799$). However, because Equation~\ref{eqn:reconstruction} is time
invariant, we may compute $Y_{s,k,\beta_s}$ in a piecewise
manner by filling in $Y_{s,k,\beta_s}$ one row at a time (using the
corresponding samples from $Y_{s, k, \alpha_s}$).

@@

To illustrate our approach, we first examine an individual held-out
raw LFP trace and its associated SuperEEG-derived reconstruction.
Figure~\ref{fig:recon}A displays the observed LFP from the red
electrode in Figure~\ref{fig:methods}A (red), and its associated
reconstruction (blue), during a 5~s time window during one of the
example patient's six recording sessions.  The two traces match
closely ($r = 0.869, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
two-dimensional histogram of the actual versus reconstructed voltages
for the entire 14.2 total hours of recordings from the example
electrode (correlation: $r = 0.909, p < 10^{-10}$).  This example confirms
that the SuperEEG algorithm recovers the recordings from this single
electrode well.  Next, we used this general approach to quantify the
algorithm's performance across the full dataset.

%sample trace & reconstruction, several frames of activity snapshot?
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/recon}
  \caption{\textbf{Observed and reconstructed LFP from a single
      electrode.} \textbf{A. Example LFP.}  A 5~s recording from the
    red electrode in Figure~\ref{fig:methods}A is displayed in red,
    and the reconstructed LFP during the same time window is shown in
    blue.  \textbf{B. Observed versus reconstructed LFP over
      14.2~hours.}  The two-dimensional histogram reflects the
    relation between distributions of observed versus reconstructed
    voltages from one patient, across the 14.2 hours of recorded data
    collected over 6 recording sessions.  The correlation reported in
    the panel is between the observed and reconstructed voltages.
    Both panels: all voltages are represented in standard deviation units
   (computed within session).}
  \label{fig:recon}
\end{figure}

@@

\section*{Discussion}
Are our brain's networks static or dynamic?  And to what extent are
the network properties of our brains stable across people and tasks?
One body of work suggests that our brain's \textit{functional}
networks are dynamic~\citep[e.g., ][]{MannEtal18},
person-specific~\citep[e.g., ][]{FinnEtal15}, and
task-specific~\citep[e.g., ][]{Turk13}.  In contrast, although the
gross anatomical structure of our brains changes meaningfully over the
course of years as our brains develop, on the timescales of typical
neuroimaging experiments (i.e., hours to days) our anatomical networks
are largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many
aspects of brain anatomy, including white matter structure, is largely
preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13,
  MoriEtal08} There are several possible means of reconciling this
apparent inconsistency between dynamic person- and task-specific
functional networks versus stable anatomical networks.  For example,
relatively small magnitude anatomical differences across people may be
reflected in reliable functional connectivity differences.  Along
these lines, one recent study found that diffusion tensor imaging
(DTI) structural data is similar across people, but may be used to
predict person-specific resting state functional connectivity
data~\citep{BeckEtal18}.  Similarly, other work indicates that
task-specific functional connectivity may be predicted by resting
state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.  Another
(potentially complementary) possibility is that our functional
networks are constrained by anatomy, but nevertheless exhibit
(potentially rapid) task-dependent changes~\citep[e.g.,
][]{SporBetz16}.

>>>>

We designed our approach to be agnostic to electrode impedances, as
electrodes that do not exist do not have impedances.  Therefore our
algorithm recovers voltages in standard deviation ($z$-scored) units
rather than attempting to recover absolute voltages. (This property
reflects the fact that $\hat{K}_{\beta_s, \alpha_s}$ and
$\hat{K}_{\alpha_s, \alpha_s}$ are correlation matrices rather than
covariance matrices.)  Also, note that
Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$
matrix, which can become computationally intractable when $T$ is very
large (e.g., for the patient highlighted in Fig.~\ref{fig:recon}, $T =
12786750$). However, because Equation~\ref{eqn:reconstruction} is time
invariant, we may compute $Y_{s,k,\beta_s}$ in a piecewise
manner by filling in $Y_{s,k,\beta_s}$ one row at a time (using the
corresponding samples from $Y_{s, k, \alpha_s}$).

@@

To illustrate our approach, we first examine an individual held-out
raw LFP trace and its associated SuperEEG-derived reconstruction.
Figure~\ref{fig:recon}A displays the observed LFP from the red
electrode in Figure~\ref{fig:methods}A (blue), and its associated
reconstruction (red), during a 5~s time window during one of the
example patient's six recording sessions.  The two traces match
closely ($r = 0.869, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
two-dimensional histogram of the actual versus reconstructed voltages
for the entire 14.2 total hours of recordings from the example
electrode (correlation: $r = 0.909, p < 10^{-10}$).  This example confirms
that the SuperEEG algorithm recovers the recordings from this single
electrode well.  Next, we used this general approach to quantify the
algorithm's performance across the full dataset.

%sample trace & reconstruction, several frames of activity snapshot?
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/recon}
  \caption{\textbf{Observed and reconstructed LFP from a single
      electrode.} \textbf{A. Example LFP.}  A 5~s recording from the
    red electrode in Figure~\ref{fig:methods}A is displayed in blue,
    and the reconstructed LFP during the same time window is shown in
    red.  \textbf{B. Observed versus reconstructed LFP over
      14.2~hours.}  The two-dimensional histogram reflects the
    relation between distributions of observed versus reconstructed
    voltages from one patient, across the 14.2 hours of recorded data
    collected over 6 recording sessions.  The correlation reported in
    the panel is between the observed and reconstructed voltages.
    Both panels: all voltages are represented in standard deviation units
   (computed within session).}
  \label{fig:recon}
\end{figure}

@@

\section*{Discussion}
Are our brain's networks static or dynamic?  And to what extent are
the network properties of our brains stable across people and tasks?
One body of work suggests that our brain's \textit{functional}
networks are dynamic~\citep[e.g., ][]{MannEtal18},
person-specific~\citep[e.g., ][]{FinnEtal15}, and
task-specific~\citep[e.g., ][]{Turk13}.  In contrast, although the
gross anatomical structure of our brains changes meaningfully over the
course of years as our brains develop, on the timescales of typical
neuroimaging experiments (i.e., hours to days) our anatomical networks
are largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many
aspects of brain anatomy, including white matter structure, are largely
preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13,
  MoriEtal08}. There are several possible means of reconciling this
apparent inconsistency between dynamic person- and task-specific
functional networks versus stable anatomical networks.  For example,
relatively small magnitude anatomical differences across people may be
reflected in reliable functional connectivity differences.  Along
these lines, one recent study found that diffusion tensor imaging
(DTI) structural data is similar across people, but may be used to
predict person-specific resting state functional connectivity
data~\citep{BeckEtal18}.  Similarly, other work indicates that
task-specific functional connectivity may be predicted by resting
state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.  Another
(potentially complementary) possibility is that our functional
networks are constrained by anatomy, but nevertheless exhibit
(potentially rapid) task-dependent changes~\citep[e.g.,
][]{SporBetz16}.
